The Near and Mid-infrared photometric properties of known redshift $z\geq5$ Quasars

### 2020-01-13 tex/MNRAS_submission/rv1/VHzQ_MNRAS_rv1.tex
Updated table 1, figure 2 and tex with up to date numbers

The breakdown of how many VH$z$Q each survey reports is given in
Table~\ref{tab:surveys}. The Sloan Digital Sky Survey (SDSS) and the
Pan-STARRS1 (PS1; PSO in Table~\ref{tab:surveys}) survey and alone
identified over half (54.6\%) of the VH$z$Q population. Data from the
Hyper Suprime-Cam (HSC) on the Subaru telescope is responsible for
13.6\% of our dataset (HSC+SHELLQs in Table~\ref{tab:surveys}). The
combination of surveys is also vital for identifying VH$z$Qs. The
UKIDSS Large Area Survey (ULAS) on its own, or in combination with
other surveys is responsible for 6.5\% of the sample (SUV+ULAS)
including the highest-$z$ object. Where more than one survey is used
for the high-redshift identification (e.g. via shorter-band veto and
longer wavelength detection) we follow the discovery paper naming
convention.

\begin{table}
\begin{tabular}{l r r l}
\hline  \hline
Survey              & \# VH$z$Qs & (\%) & Survey reference  \\
\hline  
  ATLAS             &     4    &   ( 0.86)    &  \citet{Shanks2015} \\
  CFHQS            &   20    &   ( 4.32)    &  \citet{Willott2007} \\
  DELS$^{a}$       &   16    &   ( 3.46)    &  \citet{Dey2018} \\
  ELAIS              &     1    &   ( 0.22)    &  \citet{Vaisanen2000} \\
  FIRST              &     1    &   ( 0.22)    &  \citet{Becker1995} \\
  HSC                 &    8    &   ( 1.73)    & \citet{Miyazaki2018} \\
  IMS                 &     5    &   ( 1.08)     &  \citet{Kim2015} \\
  MMT               &   12    &   ( 2.59)     &  \citet{McGreer2013} \\
  NDWFS           &     1    &   ( 0.22)    &  \citet{JD1999} \\
  PSO                 &   83   &   (17.93)   &   \citet{Kaiser2002, Kaiser2010} \\
  RD                   &     1   &   ( 0.22)    &  \citet{Mahabal2005} \\
  SDSS                &  170  &    (36.72)    & \citet{EDR} \\
 SDWISE$^{b}$    &   27    &  ( 5.83)    &   \citet{WangF2016} \\
%% SHELLQs    &  $^{c}$63  &  (13.6)   &  \citet{Matsuoka2016} \\  %% if you include 8 objects from the first HSC paper...
  SHELLQs         &    55    &   (11.88)  &  \citet{Matsuoka2016}     \\  
  SUV$^{c}$       &   20     &    ( 4.32)  & \citet{YangJ2017} \\
  UHS               &    1      &  ( 0.22)     &  \citet{WangF2017} \\
  ULAS               &   10   &   ( 2.16)     & \citet{Lawrence2007} \\
  VDES$^{d}$       &   17  &    ( 3.67)     &  \citet{Reed2017} \\
  VHS                 &     1  &     ( 0.22)    & \citet{WangF2018b} \\
  VIK                 &     9    &  ( 1.94)    &  \citet{Edge2013} \\
  VIMOS           &    1      &  ( 0.22)     &   \citet{LeFevre2003} \\
\hline  \hline
\end{tabular}
\caption{The source and number of the VH$z$Q, with the key survey reference also given. 
  Recent survey name and acronyms include: 
  $^{a}$DESI Legacy Imaging Survey; 
  $^{b}$SDWISE = SDSS+WISE; 
  $^{c}$SUV  = SDSS-ULAS/VHS; 
  $^{d}$VDES = VHS/VIKING+DES; 
%  $^{c}$Includes 8 objects with a HyperSuprimeCam \citep[HSC; ][]{Miyazaki2018} designation.
}
      \label{tab:surveys}
\end{table}

\begin{figure}
%%trim=l b r t
  \includegraphics[width=8.0cm, clip, trim=10mm 0mm 0mm 0mm]
  % {../Nofz/Nofz_0pnt075bins_20190614.pdf}
   {figures/Nofz_0pnt075bins_20190614.pdf}
  \centering
  \vspace{-12pt}
  \caption[]
  {The redshift distribution $N(z)$ of the VH$z$Q sample. 
    The bins are $\delta z=0.075$ in width and have the data 
    stacked on top of each other.}
  \label{fig:Nofz}
\end{figure}

>>>>

The breakdown of how many VH$z$Q each survey reports is given in
Table~\ref{tab:surveys}. The Sloan Digital Sky Survey (SDSS) and the
Pan-STARRS1 (PS1; PSO in Table~\ref{tab:surveys}) survey and alone
identified over half (55.5\%) of the VH$z$Q population. Data from the
Hyper Suprime-Cam (HSC) on the Subaru telescope is responsible for
13.1\% of our dataset (HSC+SHELLQs in Table~\ref{tab:surveys}). The
combination of surveys is also vital for identifying VH$z$Qs. The
UKIDSS Large Area Survey (ULAS) on its own, or in combination with
other surveys is responsible for 6.3\% of the sample (SUV+ULAS)
including the highest-$z$ object. Where more than one survey is used
for the high-redshift identification (e.g. via shorter-band veto and
longer wavelength detection) we follow the discovery paper naming
convention.

\begin{table}
\begin{tabular}{l r r l}
\hline  \hline
Survey              & \# VH$z$Qs & (\%) & Survey reference  \\
\hline  
  ATLAS             &     4    &   ( 0.82)    &  \citet{Shanks2015} \\
  CFHQS            &   20    &   ( 4.10)    &  \citet{Willott2007} \\
  DELS$^{a}$       &   16    &   ( 3.28)    &  \citet{Dey2018} \\
  ELAIS              &     1    &   ( 0.20)    &  \citet{Vaisanen2000} \\
  FIRST              &     1    &   ( 0.20)    &  \citet{Becker1995} \\
  HSC                 &    9    &   ( 1.84)    & \citet{Miyazaki2018} \\
  IMS                 &     5    &   ( 1.02)     &  \citet{Kim2015} \\
  MMT               &   12    &   ( 2.46)     &  \citet{McGreer2013} \\
  NDWFS           &     1    &   ( 0.20)    &  \citet{JD1999} \\
  PSO                 &   100   &   (20.49)   &   \citet{Kaiser2002, Kaiser2010}
  \\
  RD                   &     1   &   ( 0.20)    &  \citet{Mahabal2005} \\
  SDSS                &  171  &    (35.04)    & \citet{EDR} \\
 SDWISE$^{b}$    &   27    &  ( 5.53)    &   \citet{WangF2016} \\
%% SHELLQs    &  $^{c}$63  &  (13.6)   &  \citet{Matsuoka2016} \\  %% if you include 8 objects from the first HSC paper...
  SHELLQs         &    55    &   (11.27)  &  \citet{Matsuoka2016}     \\  
  SUV$^{c}$       &   21     &    (4.30)  & \citet{YangJ2017} \\
  TGSS				&	1		&	(0.20)	& \citet{Saxena2018} \\
  TN				& 	1		&	(0.20)	& ?? \citet{vanBreugel1999} \\
  UHS               &    1      &  ( 0.20)     &  \citet{WangF2017} \\
  ULAS               &   10   &   ( 2.05)     & \citet{Lawrence2007} \\
  VDES$^{d}$       &   17  &    ( 3.48)     &  \citet{Reed2017} \\
  VHS                 &     1  &     ( 0.20)    & \citet{WangF2018b} \\
  VIK                 &     10    &  ( 2.05)    &  \citet{Edge2013} \\
  VIMOS           &    1      &  ( 0.20)     &   \citet{LeFevre2003} \\
  XMM				& 	1	&	 (0.20)		& \citet{Khorunzhev2017} \\
\hline  \hline
\end{tabular}
\caption{The source and number of the VH$z$Q, with the key survey reference also given. 
  Recent survey name and acronyms include: 
  $^{a}$DESI Legacy Imaging Survey; 
  $^{b}$SDWISE = SDSS+WISE; 
  $^{c}$SUV  = SDSS-ULAS/VHS; 
  $^{d}$VDES = VHS/VIKING+DES; 
%  $^{c}$Includes 8 objects with a HyperSuprimeCam \citep[HSC; ][]{Miyazaki2018} designation.
}
      \label{tab:surveys}
\end{table}

\begin{figure}
%%trim=l b r t
  \includegraphics[width=8.0cm, clip, trim=10mm 0mm 0mm 0mm]
  % {../Nofz/Nofz_0pnt075bins_20190614.pdf}
   {figures/Nofz_0pnt075bins_20200113.pdf}
  \centering
  \vspace{-12pt}
  \caption[]
  {The redshift distribution $N(z)$ of the VH$z$Q sample. 
    The bins are $\delta z=0.075$ in width and have the data 
    stacked on top of each other.}
  \label{fig:Nofz}
\end{figure}
